Rapid technological progress in white light-emitting diodes and its sources in innovation and technology spillovers

### 2023-10-05 2_SSL_NE/article/article_main.tex
added data availability statement

>>>>

\subsection{Data Availability}

The manufacturing cost model and associated input data is available are the Zenodo repository with the identifier DOI: 10.5281/ZENODO.8410658) \cite{zenodo_costmodel}. The Python scripts that were used to compute the light quality metrics of \cref{fgr:consumer_experience} are available in the Zenodo repository with the identifier DOI: 10.5281/ZENODO.8410789 \cite{zenodo_lightquality}.
